On the uniqueness and stability of dictionaries \\ for sparse representation of noisy signals

### 2019-05-10 manuscripts/IEEE/final_submission.tex
fixed

% WITHOUT J SUBSCRIPT
We begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\mathbf{A}$ satisfies \eqref{SparkCondition} and \mbox{$\varepsilon < L_{2k}\mathbf{A} / C_1$}, assuming that $\overline m = m$ (without loss of generality) so as to omit an otherwise requisite subscript $(\cdot)_J$ around certain matrices and vectors.
Consider any $2k$-sparse $\mathbf{x} \in \mathbb{R}^m$ and note that $\|\mathbf{x}\|_1 \leq \sqrt{2k}  \|\mathbf{x}\|_2$. By definition of $L_{2k}$ in \eqref{Ldef}, we have:
\begin{align}\label{stuff}
\|\mathbf{x} - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x} \|_1 \nonumber
&\leq \frac{\|\mathbf{BPD}(\mathbf{x} - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x})\|_2}{L_{2k}(\mathbf{BPD})} \\ \nonumber
&\leq \frac{\|( \mathbf{BPD} - \mathbf{A}) \mathbf{x}\|_2 + \|\mathbf{A}\mathbf{x} - \mathbf{B}\mathbf{\overline x}\|_2}{L_{2k}(\mathbf{BPD})} \\
&\leq \frac{C_1\varepsilon \|\mathbf{x}\|_1 + \varepsilon}{L_{2k}(\mathbf{BPD})},
\end{align}
%\begin{align}\label{stuff}
%\frac{ \|\mathbf{x} - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x} \|_1 } { \|\mathbf{D}^{-1}\|_1 }  \
%&\leq \|\mathbf{Dx} - \mathbf{P}^{\top}\mathbf{\overline x} \|_1 \\ \nonumber
%&\leq \frac{\|\mathbf{BP}(\mathbf{D}\mathbf{x} - \mathbf{P}^{\top}\mathbf{\overline x})\|_2}{L_{2k}(\mathbf{BP})} \\ \nonumber
%&\leq \frac{\|( \mathbf{BPD} - \mathbf{A}) \mathbf{x}\|_2 + \|\mathbf{A}\mathbf{x} - \mathbf{B}\mathbf{\overline x}\|_2}{L_{2k}(\mathbf{BP})} \\
%&\leq \frac{C_1\varepsilon \|\mathbf{x}\|_1 + \varepsilon}{L_{2k}(\mathbf{BP})},
%\end{align}
where the term $C_1\varepsilon \|\mathbf{x}\|_1$ in the numerator above follows from the triangle inequality and \eqref{Cstable}.

It remains for us to bound the denominator.  By the triangle inequality:
\begin{align*}
\|\mathbf{BPD}\mathbf{x}\|_2 
&\geq \|\mathbf{A}\mathbf{x}\|_2 - \|(\mathbf{A} - \mathbf{BPD})\mathbf{x}\|_2 \\
&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{x}\|_2,
\end{align*}

>>>>

% WITHOUT J SUBSCRIPT
We begin our proof of Thm.~\ref{DeterministicUniquenessTheorem} by showing how dictionary recovery \eqref{Cstable} already implies sparse code recovery \eqref{b-PDa} when $\mathbf{A}$ satisfies \eqref{SparkCondition} and \mbox{$\varepsilon < L_{2k}\mathbf{A} / C_1$}, assuming that $\overline m = m$ (without loss of generality) so as to omit an otherwise requisite subscript $(\cdot)_J$ around certain matrices and vectors. By definition of $L_{2k}$ in \eqref{Ldef}, we have for all $i \in [N[$:
\begin{align}\label{stuff}
\|\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i \|_1 \nonumber
&\leq \frac{\|\mathbf{BPD}(\mathbf{x}_i - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x}_i)\|_2}{L_{2k}(\mathbf{BPD})} \\ \nonumber
&\leq \frac{\|( \mathbf{BPD} - \mathbf{A}) \mathbf{x}_i\|_2 + \|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2}{L_{2k}(\mathbf{BPD})} \\
&\leq \frac{C_1\varepsilon \|\mathbf{x}_i\|_1 + \varepsilon}{L_{2k}(\mathbf{BPD})},
\end{align}
%\begin{align}\label{stuff}
%\frac{ \|\mathbf{x} - \mathbf{D}^{-1}\mathbf{P}^{\top}\mathbf{\overline x} \|_1 } { \|\mathbf{D}^{-1}\|_1 }  \
%&\leq \|\mathbf{Dx} - \mathbf{P}^{\top}\mathbf{\overline x} \|_1 \\ \nonumber
%&\leq \frac{\|\mathbf{BP}(\mathbf{D}\mathbf{x} - \mathbf{P}^{\top}\mathbf{\overline x})\|_2}{L_{2k}(\mathbf{BP})} \\ \nonumber
%&\leq \frac{\|( \mathbf{BPD} - \mathbf{A}) \mathbf{x}\|_2 + \|\mathbf{A}\mathbf{x} - \mathbf{B}\mathbf{\overline x}\|_2}{L_{2k}(\mathbf{BP})} \\
%&\leq \frac{C_1\varepsilon \|\mathbf{x}\|_1 + \varepsilon}{L_{2k}(\mathbf{BP})},
%\end{align}
where the term $C_1\varepsilon \|\mathbf{x}_i\|_1$ in the numerator above follows from the triangle inequality and \eqref{Cstable}.

It remains for us to bound the denominator. For any $2k$-sparse $\mathbf{x}$, we have by the triangle inequality:
\begin{align*}
\|\mathbf{BPD}\mathbf{x}\|_2 
&\geq \|\mathbf{A}\mathbf{x}\|_2 - \|(\mathbf{A} - \mathbf{BPD})\mathbf{x}\|_2 \\
&\geq \sqrt{2k} (L_{2k}(\mathbf{A}) -  C_1\varepsilon) \|\mathbf{x}\|_2,
\end{align*}
